Revisiting `Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation

### 2023-05-19 analysis/quarto/paper.qmd
work on introduction

@GKLS2020 find that standard public good games do not generalize well to real-world climate action. They also find that generalizability depends on structural resemblance of the public goods game with the context of climate change mitigation. Greater resemblance improves generalizability. Because GMTV's dynamic setting has a more realistic property—namely, interdependencies—one wonders whether it is better suited to inform public policy. To approach this question, I ran the experiment with different samples^[GMTV ran their experiments with students in Nottingham, England.] and
<!--, that is, with participants who make their decisions in an environment which is more natural than the lab.-->
observed the participants' behavior in voluntary climate actions (VCA). This yielded a setting similar to @GKLS2020's which allows me to analyze how behavior in the abstract game translates into real-world action across samples.

@@

@AGM2018 conducted public good games in the lab and on MTurk to draw lessons from online experimentation. This study extends this literature [see also @GoodmanPaolacci2017  @AmirEtAl2012] by focusing on a completely inexperienced sample that has not been exposed to interactive experiments before. This required me to design a robust (and thus, more complex) software to minimize attrition. In exchange, the online setting allowed me to also collect paradata to assess the fluency and feasibility of the experiment. This article reports on both topics: the robust design as well as the feasibility.

Taken together, this study makes three contributions. First, it reproduces parts of GMTV's original experiment and highlights the importance of pure replications. Second, it shows that logistically complex online experiments are feasible for samples other than students or clickworkers. Third, this paper supports critics arguing that findings from abstract games do not generalize well---not even with a more representative sample. After reporting the methods, this paper is organized along these findings.

# Transparency

@@

Accordingly, I  changed many of the analysis scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] However, because the originally planned analysis code is archived and reproducible, these changes are transparent. Importantly, I followed a literate programming approach [@Knuth_1984; @AkhtarYe_2023]. Hence, all documents needed to analyze the data and write the report stem from the same source. This establishes consistence between the commands one tells the statistical software to do and the explanation one tells human beings one told the statistical software to do. As such, (a), (b) and the transition from (a) to (b) are not only transparent but also comprehensible.

@@

>>>>

@GKLS2020 find that standard public good games do not generalize well to real-world climate action. They also find that generalizability depends on structural resemblance of the public goods game with the context of climate change mitigation. Greater resemblance improves generalizability. Because GMTV's dynamic setting has a more realistic property—namely, interdependencies—one wonders whether it is better suited to inform public policy. To approach this question, I ran the experiment with different samples^[GMTV ran their experiments with students in Nottingham, England.] and
<!--, that is, with participants who make their decisions in an environment which is more natural than the lab.-->
observed the participants' behavior in voluntary climate actions (VCA). This yielded a setting similar to @GKLS2020's which allows me to analyze how behavior in the abstract game translates into real-world action across samples. The article shows that the dynamic setting _does not_ add any advances with respect to generalizability of results.

@@

@AGM2018 conducted public good games in the lab and on MTurk to draw lessons from online experimentation. This study extends this literature [see also @GoodmanPaolacci2017  @AmirEtAl2012] by focusing on an inconvenient sample: one that is completely inexperienced sample that has not been exposed to interactive experiments before. This required me to design a robust (and thus, more complex) software to minimize attrition. In exchange, the online setting allowed me to also collect paradata to assess the fluency and feasibility of the experiment. This article reports on both topics: the robust design as well as the feasibility.

Taken together, this study makes three contributions. First, it reproduces parts of GMTV's original experiment and highlights the importance of pure replications. Second, it shows that logistically complex online experiments are feasible for samples other than students or clickworkers. Third, this paper supports critics arguing that findings from abstract games do not generalize well---not even with a more representative sample.

After commenting on transparent research practices and reporting the methods in @sec-transparency and @sec-methods, this paper is organized along these findings: The confirmatory reproduction is reported in @sec-replication, the online feasibility in @sec-feasibility and the generalizability in @sec-generalizability. @sec-conclusion concludes.

# Transparency {#sec-transparency}

@@

Accordingly, I  changed many of the analysis scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] However, because the originally planned analysis code is archived and reproducible, these changes are transparent. Importantly, I followed a literate programming approach [@Knuth_1984; @AkhtarYe_2023]. Hence, all documents needed to analyze the data and to write the report stem from the same source. This establishes consistence between the commands one tells the statistical software to do and the explanation one tells human beings one told the statistical software to do. As such, (a), (b) and the transition from (a) to (b) are not only transparent but also comprehensible.

@@

Limitations?

### 2023-05-19 analysis/quarto/paper.tex
work on introduction

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public good game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, frame hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

\citet{GKLS2020} find that standard public good games do not generalize
well to real-world climate action. They also find that generalizability
depends on structural resemblance of the public goods game with the
context of climate change mitigation. Greater resemblance improves
generalizability. Because GMTV's dynamic setting has a more realistic
property---namely, interdependencies---one wonders whether it is better
suited to inform public policy. To approach this question, I ran the
experiment with different samples\footnote{GMTV ran their experiments
  with students in Nottingham, England.} and observed the participants'
behavior in voluntary climate actions (VCA). This yielded a setting
similar to \citet{GKLS2020}'s which allows me to analyze how behavior in
the abstract game translates into real-world action across samples.

@@

\citet{AGM2018} conducted public good games in the lab and on MTurk to
draw lessons from online experimentation. This study extends this
literature \citep[see also][ \citet{AmirEtAl2012}]{GoodmanPaolacci2017}
by focusing on a completely inexperienced sample that has not been
exposed to interactive experiments before. This required me to design a
robust (and thus, more complex) software to minimize attrition. In
exchange, the online setting allowed me to also collect paradata to
assess the fluency and feasibility of the experiment. This article
reports on both topics: the robust design as well as the feasibility.

Taken together, this study makes three contributions. First, it
reproduces parts of GMTV's original experiment and highlights the
importance of pure replications. Second, it shows that logistically
complex online experiments are feasible for samples other than students
or clickworkers. Third, this paper supports critics arguing that
findings from abstract games do not generalize well---not even with a
more representative sample. After reporting the methods, this paper is
organized along these findings.

\hypertarget{transparency}{%
\section{Transparency}\label{transparency}}

@@

Accordingly, I changed many of the analysis scripts.\footnote{The source
  code of this document contains the analysis and can be found
  \href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}{here}:
  https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}
However, because the originally planned analysis code is archived and
reproducible, these changes are transparent. Importantly, I followed a
literate programming approach \citep{Knuth_1984, AkhtarYe_2023}. Hence,
all documents needed to analyze the data and write the report stem from
the same source. This establishes consistence between the commands one
tells the statistical software to do and the explanation one tells human
beings one told the statistical software to do. As such, (a), (b) and
the transition from (a) to (b) are not only transparent but also
comprehensible.

>>>>

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public good game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, sharp corners, borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi

@@

\citet{GKLS2020} find that standard public good games do not generalize
well to real-world climate action. They also find that generalizability
depends on structural resemblance of the public goods game with the
context of climate change mitigation. Greater resemblance improves
generalizability. Because GMTV's dynamic setting has a more realistic
property---namely, interdependencies---one wonders whether it is better
suited to inform public policy. To approach this question, I ran the
experiment with different samples\footnote{GMTV ran their experiments
  with students in Nottingham, England.} and observed the participants'
behavior in voluntary climate actions (VCA). This yielded a setting
similar to \citet{GKLS2020}'s which allows me to analyze how behavior in
the abstract game translates into real-world action across samples. The
article shows that the dynamic setting \emph{does not} add any advances
with respect to generalizability of results.

@@

\citet{AGM2018} conducted public good games in the lab and on MTurk to
draw lessons from online experimentation. This study extends this
literature \citep[see also][ \citet{AmirEtAl2012}]{GoodmanPaolacci2017}
by focusing on an inconvenient sample: one that is completely
inexperienced sample that has not been exposed to interactive
experiments before. This required me to design a robust (and thus, more
complex) software to minimize attrition. In exchange, the online setting
allowed me to also collect paradata to assess the fluency and
feasibility of the experiment. This article reports on both topics: the
robust design as well as the feasibility.

Taken together, this study makes three contributions. First, it
reproduces parts of GMTV's original experiment and highlights the
importance of pure replications. Second, it shows that logistically
complex online experiments are feasible for samples other than students
or clickworkers. Third, this paper supports critics arguing that
findings from abstract games do not generalize well---not even with a
more representative sample.

After commenting on transparent research practices and reporting the
methods in Section~\ref{sec-transparency} and Section~\ref{sec-methods},
this paper is organized along these findings: The confirmatory
reproduction is reported in Section~\ref{sec-replication}, the online
feasibility in Section~\ref{sec-feasibility} and the generalizability in
Section~\ref{sec-generalizability}. Section~\ref{sec-conclusion}
concludes.

\hypertarget{sec-transparency}{%
\section{Transparency}\label{sec-transparency}}

@@

Accordingly, I changed many of the analysis scripts.\footnote{The source
  code of this document contains the analysis and can be found
  \href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}{here}:
  https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}
However, because the originally planned analysis code is archived and
reproducible, these changes are transparent. Importantly, I followed a
literate programming approach \citep{Knuth_1984, AkhtarYe_2023}. Hence,
all documents needed to analyze the data and to write the report stem
from the same source. This establishes consistence between the commands
one tells the statistical software to do and the explanation one tells
human beings one told the statistical software to do. As such, (a), (b)
and the transition from (a) to (b) are not only transparent but also
comprehensible.
